---
title: "Data_generate_for_sas"
author: "Junting Ren"
date: "9/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(splines)
library(MASS)
library(tidyverse)
library(doParallel) # for parallel computing
library(gridExtra)
library(grid)
library(matrixStats)
source("../../functions/sim_fcns_probit.R")

```


# Generating from a generalized gamma model
Code from https://rpubs.com/FJRubio/GG
```{r}
# theta   : scale parameter
# kappa      : shape parameter
# delta   : shape parameter
# t       : positive argument   
# p       : probability (0,1)
# n       : number of simulations

# Probability Density Function
dggamma <- function(t, theta, kappa, delta, log = FALSE){
  val <- log(delta) - kappa*log(theta) - lgamma(kappa/delta) + (kappa - 1)*log(t) -
  (t/theta)^delta
  if(log) return(val) else return(exp(val))
}

# GG CDF
pggamma <- function(t, theta, kappa, delta, log.p = FALSE){
  val <- pgamma( t^delta, shape = kappa/delta, scale = theta^delta, log.p = TRUE) 
  if(log.p) return(val) else return(exp(val))
}

# GG Survival Function
sggamma <- function(t, theta, kappa, delta, log.p = FALSE){
  val <- pgamma( t^delta, shape = kappa/delta, scale = theta^delta, log.p = TRUE, lower.tail =  FALSE) 
  if(log.p) return(val) else return(exp(val))
}


# GG Hazard Function
hggamma <- function(t, theta, kappa, delta, log = FALSE){
  val <- dggamma(t, theta, kappa, delta, log = TRUE) - sggamma(t, theta, kappa, delta, log.p = TRUE)
  if(log) return(val) else return(exp(val))
}

# GG Cumulative Hazard Function
chggamma <- function(t, theta, kappa, delta){
  val <- -pgamma( t^delta, shape = kappa/delta, scale = theta^delta, log.p = TRUE, lower.tail =  FALSE) 
  return(val) 
}

# Quantile Function
qggamma <- function(p, theta, kappa, delta){
  out <- qgamma(p, shape = kappa/delta, scale = theta^delta)^(1/delta)
  return(out)
}

# Random number Generation Function
rggamma <- function(n, theta, kappa, delta){
  p <- runif(n)
  out <- qgamma(p, shape = kappa/delta, scale = theta^delta)^(1/delta)
  return(as.vector(out))
}
```


Generating generalized Gamma distribution
```{r}
n_data = 500
write_dat = T
read_dat = T
trunc_end = 100
MCMC_mean = T
n = 2000
k = 0.7
gamma = c(1,1.2,-1)
alpha = c(0.3,1,-0.5)
delta_coef = c(-0.3,-0.5,-0.2)
data_file_name = paste("./data_gamma/dat_out_gamma_", "n_dat=", n_data, "_n=",n, ".csv", sep = "")
if(!read_dat){
  data_out_gamma = data.frame()
  for(j in 1:n_data){
    x0 = rep(1,n)
    x1 = rnorm(n, mean = 0, sd = 1)
    #x1 = rbinom(n, 1, 0.5)
    x2 = rbinom(n, 1, 0.5)
    
    dat_matrix = matrix(cbind(x0,x1,x2),n,3)
    # gamma = c(1,1.2,-1)
    # alpha = c(0.3,1,-0.5)
    # delta_coef = c(-0.3,-0.5,-0.2)
    #alpha = c(2.4,0.95,-1.42)
    #delta_coef = c(0.6,-0.11,-0.2)
    p = pnorm( dat_matrix%*%as.vector(gamma))
    indicator = rbinom(n, size = 1, prob = p)
    
    
    mu = dat_matrix %*% as.vector(alpha)
    sigma = sqrt(exp(dat_matrix %*% as.vector(delta_coef)))
    delta = k/sigma
    theta = exp(mu)/((1/k^2)^(sigma/k))
    kappa = 1/(sigma*k)
    
    
    z = c()
    for(i in 1:n){
      if(indicator[i]==1){
        z[i]=rggamma(1, theta[i], kappa[i], delta[i])
      }else{
        z[i]=0
      }
    }
    
    data_out_gamma_single = cbind(z, dat_matrix, j)
    colnames(data_out_gamma_single) = c("z", "x0", "x1", "x2","num")
    data_out_gamma = rbind(data_out_gamma, data_out_gamma_single)
  }
  if(write_dat){
    write.csv(data_out_gamma, file = data_file_name, row.names = F)
  }
}else{
  data_out_gamma = read_csv(data_file_name)
}

```

Function for calculate the gamma mean
```{r}
cal_mean_gamma = function(mu, sigma, k){
  exp(
    mu+sigma*log(k^2)/k+log((gamma(1/k^2+sigma/k)))-log(gamma(1/k^2))
  )
}

#Monte Carlo simulation to obtain the true quantiles
cal_quantile_zero_infl_gamma = function(x, gamma, alpha,delta_coef, k, n =500000, quantiles = c(0.5, 0.75), trunc_end = Inf){
  p = pnorm( x%*%as.vector(gamma))
  indicator = rbinom(n, size = 1, prob = p)
  
  
  k = k
  mu = x %*% as.vector(alpha)
  sigma = sqrt(exp(x %*% as.vector(delta_coef)))
  delta = k/sigma
  theta = exp(mu)/((1/k^2)^(sigma/k))
  kappa = 1/(sigma*k)
  
  
  z = c()
  for(i in 1:n){
    if(indicator[i]==1){
      z[i]=rggamma(1, theta, kappa, delta)
    }else{
      z[i]=0
    }
  }
  z = z[z < trunc_end]
  q_v = c()
  for(i in 1:length(quantiles)){
    q_v[i] = quantile(z, probs = quantiles[i])
  }
  mean_q = mean(z)
  return(list(quantiles_value = q_v, quantiles = quantiles, mean= mean_q))
  
}

```

Calculate the mean,median, 0.75 for baseline 
```{r}
effect_mean = c()
effect_median = c()
effect_75 = c()



q = cal_quantile_zero_infl_gamma(x = c(1,0,0), gamma = gamma, alpha = alpha, delta_coef = delta_coef ,k = k, trunc_end = Inf)
effect_median = c(effect_median, q$quantiles_value[1])
effect_75 = c(effect_75,q$quantiles_value[2])
if(!MCMC_mean){
  mu = alpha[1]
  sigma =sqrt(exp(delta_coef[1]/2))
  (baseline = pnorm(gamma[1])*cal_mean_gamma(mu, sigma, k = k))
  effect_mean = c(effect_mean, baseline)
}else{
  effect_mean = c(effect_mean, q$mean)
}

```

Calculate the mean increase for one unit increase in x1
```{r}
q1 = cal_quantile_zero_infl_gamma(x = c(1,1,0), gamma = gamma, alpha = alpha, delta_coef = delta_coef ,k = k, trunc_end = Inf)
effect_median = c(effect_median, q1$quantiles_value[1] - effect_median[1])
effect_75 = c(effect_75,q1$quantiles_value[2] - effect_75[1])
if(!MCMC_mean){
  mu = alpha[1]+ alpha[2]
  sigma =sqrt( exp((delta_coef[1]+delta_coef[2])/2))
  (increase_x1_mean = pnorm(gamma[1]+gamma[2])*cal_mean_gamma(mu, sigma, k = k)-baseline)
  effect_mean = c(effect_mean, increase_x1_mean)
}else{
  effect_mean = c(effect_mean, q1$mean - effect_mean[1])
}
```


Calculate the mean increase for one unit increase in x2
```{r}
q2 = cal_quantile_zero_infl_gamma(x = c(1,0,1), gamma = gamma, alpha = alpha, delta_coef = delta_coef ,k = k,  trunc_end = Inf)
effect_median = c(effect_median, q2$quantiles_value[1] - effect_median[1])
effect_75 = c(effect_75,q2$quantiles_value[2] - effect_75[1])
if(!MCMC_mean){
  mu = alpha[1]+ alpha[3]
sigma = sqrt(exp((delta_coef[1]+delta_coef[3])/2))
(increase_x2_mean = pnorm(gamma[1]+gamma[3])*cal_mean_gamma(mu, sigma, k = k)-baseline)
effect_mean = c(effect_mean, increase_x2_mean)
}else{
  effect_mean = c(effect_mean, q2$mean - effect_mean[1])
}
```




```{r}
trunc_end = quantile(data_out_gamma$z[data_out_gamma$z > 0], probs = 0.99)
data_out_gamma = data_out_gamma %>% filter(z<trunc_end)

dat_test  = data_out_gamma %>% filter(num == 5) 
Z = dat_test$z
X = data.matrix(select(dat_test, x0,x1,x2))
hist(Z)
```



```{r}
K_model=10
G = NULL
nIter = 2000
burnIn = 1000
thin = 1
byStep = 0.01
useCov = T
repara_lambda = T
specify_knot = F
intercept = T
internal_knots = NULL
quantile_z = quantile(data_out_gamma$z[data_out_gamma$z > 0], probs = 0.99)
if(K_model > 8 & specify_knot ==T ){
  # internal_knots = c(seq(byStep, quantile_z,
  #                        length.out = (K_model)-ceiling((K_model)*0.2)),
  #                    seq(quantile_z, max(Z),
  #                        length.out = ceiling((K_model)*0.2+1))[-1])
  # internal_knots = internal_knots[-length(internal_knots)]
  # internal_knots = internal_knots[-1]
  # internal_knots = c(quantile(
  #                   Z[Z!=0 & Z<quantile_z],
  #                        seq(0,1,length.out = (K_model)-ceiling((K_model)*0.2))),
  #                   seq(quantile_z, max(Z),
  #                       length.out = ceiling((K_model)*0.2+1))[-1])
  # internal_knots = internal_knots[-length(internal_knots)]
  # internal_knots = internal_knots[-1]
  
  internal_knots = quantile(
    Z[Z!=0 & Z<quantile_z],
    seq(0,1,length.out = K_model))
  internal_knots = internal_knots[-length(internal_knots)]
  internal_knots = internal_knots[-1]
  # internal_knots = quantile(Z[Z!=0], seq(0,1,length.out = K_model))
  # internal_knots = internal_knots[-1]
  # internal_knots = internal_knots[-length(internal_knots)]
}else{
  specify_knot = F
  internal_knots = NULL
}

step_thres = 0.2
s_theta = 2 
gamma_prior_var  = 2.5
alpha_prior_var = 100
source("../../functions/Bayesian_Semi.R") #B-spline with intercept
source("../../functions/output_fcns.R")
source("../../functions/sim_fcns.R")
source("../../functions/fcns_rf.R")
source("../../functions/Bdensity.R")
#MCMCfit1<-Bayesian_Semi_probit(Z,X,G,K=K_model,nIter,burnIn,thin, useCov=useCov,  byStep=byStep,max_Z = max(Z),c = 0.01, d = 0.01, alpha_prior_var = alpha_prior_var, gamma_prior_var=gamma_prior_var, step_thres = step_thres, repara_lambda = repara_lambda,specify_knot = specify_knot, s_theta = s_theta, internal_knots = internal_knots, intercept = intercept)
MCMCfit1<-Bayesian_Semi(Z,X,G,K=K_model,nIter,burnIn,thin, useCov=useCov,  byStep=byStep,max_Z = max(Z),c = 0.01, d = 0.01)
```

```{r}
source("../../functions/output_fcns_probit.R")
draw_b_spline(MCMCfit1)
```


```{r}
MCMCfit = MCMCfit1
convergence_plot(MCMCfit, save=F) 
```

```{r}
last_n = 1000
# True parameters
true_para = list(effect_mean = effect_mean, effect_median = effect_median, 
                 effect_0.75 = effect_75)
#Print out the table
(parameter_est = meanCI(MCMCfit1,level = 0.05,true_para = true_para,last_n = last_n, return_all = F))
```


## Start the simulation
```{r}
# Cores
cl <- makeCluster(detectCores()-1)
folder_path = "./result_b_spline/"
dat_name = paste(folder_path, "compare_gamma", "n=",n,"_","K_model = ",K_model ,"_", "logistic","_",Sys.Date(), ".RData", sep = "")
table_name = paste(folder_path, "table_compare_gamma", "n=",n,"_", "K_model = ",K_model ,"_","logistic","_", Sys.Date(), ".csv", sep = "")
```

Simualtion html name
```{r}
paste("compare_gamma", "n=",n,"_", "K_model = ",K_model ,"_","logistic","_",Sys.Date(), sep = "")
```

```{r}
check_para = list(Alpha = NULL, Gamma = NULL,
                  effect_mean = effect_mean, 
                  effect_median = effect_median,
                  effect_0.25 = 0,
                  effect_0.75 = effect_75,
                  effect_dist = 0)
registerDoParallel(cl)
cover_list_list = foreach(t=1:n_data,
                          .errorhandling = "pass", 
                          .inorder = F,.verbose	=T) %dopar% {
                            list_simdata = data_out_gamma[data_out_gamma$num==t,]
                            Z = list_simdata$z
                            G = list_simdata$G
                            X = list_simdata[,c("x0", "x1", "x2")]
                            X=data.matrix(X)
                            N=length(Z)
                            if(K_model > 8 & specify_knot ==T ){
                              # internal_knots = c(quantile(
                              #   Z[Z!=0 & Z<quantile_z],
                              #   seq(0,1,length.out = (K_model)-ceiling((K_model)*0.2))),
                              #   seq(10, max(Z),
                              #       length.out = ceiling((K_model)*0.2+1))[-1])
                              # internal_knots = internal_knots[-length(internal_knots)]
                              # internal_knots = internal_knots[-1]
                              internal_knots = quantile(
                                Z[Z!=0 & Z<quantile_z],
                                seq(0,1,length.out = K_model))
                              internal_knots = internal_knots[-length(internal_knots)]
                              internal_knots = internal_knots[-1]
                              # internal_knots = c(seq(byStep, quantile_z,
                              #                        length.out = (K_model)-ceiling((K_model)*0.2)),
                              #                    seq(quantile_z, max(Z),
                              #                        length.out = ceiling((K_model)*0.2+1))[-1])
                              # internal_knots = internal_knots[-length(internal_knots)]
                              # internal_knots = internal_knots[-1]
                            }else{
                              specify_knot = F
                              internal_knots = NULL
                            }
                            Bayesian_Semi(Z,X,G,K=K_model,nIter,burnIn,thin, useCov=useCov,  byStep=byStep,max_Z = max(Z),c = 0.01, d = 0.01, check_para = check_para)
                          }

GMN_list = lapply(cover_list_list,function(x)x$GMN)
AMN_list = lapply(cover_list_list,function(x)x$AMN)
thres_list = lapply(cover_list_list,function(x)x$thres_mean)
mean_list = lapply(cover_list_list,function(x)x$effect_mean)
median_list = lapply(cover_list_list,function(x)x$effect_median)
perc.25_list = lapply(cover_list_list,function(x)x$effect_0.25)
perc.75_list = lapply(cover_list_list,function(x)x$effect_0.75)
dist_list = lapply(cover_list_list,function(x)x$effect_dist)
AMN_cover = lapply(cover_list_list,function(x)x$cover_alpha)
thres_cover = lapply(cover_list_list,function(x)x$cover_thres)
GMN_cover = lapply(cover_list_list,function(x)x$cover_gamma)
mean_cover = lapply(cover_list_list,function(x)x$cover_mean)
median_cover = lapply(cover_list_list,function(x)x$cover_median)
perc.25_cover = lapply(cover_list_list,function(x)x$cover_0.25)
perc.75_cover = lapply(cover_list_list,function(x)x$cover_0.75)
dist_cover = lapply(cover_list_list,function(x)x$cover_dist)
sigma_delta_sq_mean_list = lapply(cover_list_list,function(x)x$sigma_delta_sq_mean)
sigma_delta_sq_cover = lapply(cover_list_list,function(x)x$cover_sigma_delta_sq)
Sigma_eta_mean_list = lapply(cover_list_list,function(x)x$Sigma_eta_mean)
Sigma_eta_cover= lapply(cover_list_list,function(x)x$cover_Sigma_eta)

length_before = length(mean_cover)
if(write_dat){
  save.image(file=dat_name)
}
```

Filter out the null simulations
```{r}
GMN_list = Filter(Negate(is.null), GMN_list)
AMN_list = Filter(Negate(is.null), AMN_list)
thres_list = Filter(Negate(is.null), thres_list)
AMN_cover = Filter(Negate(is.null), AMN_cover)
thres_cover = Filter(Negate(is.null), thres_cover)
GMN_cover = Filter(Negate(is.null), GMN_cover)
mean_list = Filter(Negate(is.null), mean_list)
median_list = Filter(Negate(is.null), median_list)
perc.25_list = Filter(Negate(is.null), perc.25_list)
perc.75_list = Filter(Negate(is.null), perc.75_list)
dist_list = Filter(Negate(is.null), dist_list)
mean_cover = Filter(Negate(is.null), mean_cover)
median_cover = Filter(Negate(is.null), median_cover)
perc.25_cover = Filter(Negate(is.null), perc.25_cover)
perc.75_cover = Filter(Negate(is.null), perc.75_cover)
dist_cover = Filter(Negate(is.null), dist_cover)
sigma_delta_sq_mean_list = Filter(Negate(is.null), sigma_delta_sq_mean_list)
sigma_delta_sq_cover = Filter(Negate(is.null), sigma_delta_sq_cover)
Sigma_eta_mean_list = Filter(Negate(is.null), Sigma_eta_mean_list)
Sigma_eta_cover = Filter(Negate(is.null), Sigma_eta_cover)

length_after =  length(perc.75_cover)
print("# of simulation filter out")
length_before - length_after
```

```{r}
#Cover rate
print("Global mean cover rate")
Reduce("+", mean_cover)/length(mean_cover)
print("Global median cover rate")
Reduce("+", median_cover)/length(median_cover)
print("Global 0.25 perc cover rate")
Reduce("+", perc.25_cover)/length(perc.25_cover)
print("Global 0.75 perc cover rate")
Reduce("+", perc.75_cover)/length(perc.75_cover)
print("Distribution quantity cover rate:  mean   median  perc.25  perc.75 ")
Reduce("+", dist_cover)/length(dist_cover)
print("Alpha cover rate")
Reduce("+", AMN_cover)/length(AMN_cover)
print("Thres cover rate")
Reduce("+", thres_cover)/length(thres_cover)
print("Gamma cover rate")
Reduce("+", GMN_cover)/length(GMN_cover)

#Mean
print("Global mean")
Reduce("+", mean_list)/length(mean_list)
print("Global mean true")
check_para$effect_mean

print("Global median")
Reduce("+", median_list)/length(median_list)
print("Global median true")
check_para$effect_median

print("Global perc 0.25")
Reduce("+", perc.25_list)/length(perc.25_list)
print("Global prec 0.25 true")
check_para$effect_0.25

print("Global perc 0.75")
Reduce("+", perc.75_list)/length(perc.75_list)
print("Global 0.75 true")
check_para$effect_0.75
print("Dist quantity mean")
Reduce("+", dist_list)/length(dist_list)
print("Distribution quantity true")
check_para$effect_dist

print("Alpha mean")
Reduce("+", AMN_list)/length(AMN_list)
print("True Alpha")
check_para$Alpha
print("Thres mean")
Reduce("+", thres_list)/length(thres_list)
print("True thres")
check_para$thres
print("Gamma mean")
Reduce("+", GMN_list)/length(GMN_list)
print("True Gamma")
check_para$Gamma
print("Sigma_delta_sq cover rate")
mean(unlist(sigma_delta_sq_cover))
print("Mean Sigma_delta_sq_mean")
mean(unlist(sigma_delta_sq_mean_list))
print("true Sigma_delta_sq")
check_para$sigma_b_delta^2
print("Simga_eta cover rate")
mean(unlist(Sigma_eta_cover))
print("Mean Simga_eta_mean")
mean(unlist(Sigma_eta_mean_list))
print("true Sigma_eta_square")
check_para$Sigma_b_eta^2
```

Gamma bias
```{r}
Reduce("+", GMN_list)/length(GMN_list)-check_para$Gamma
```

Gamma sd
```{r}
sqrt(
  Reduce("+", lapply(GMN_list, "^", 2)) / length(GMN_list) - 
       (Reduce("+", GMN_list)/length(GMN_list))^2
  )
```

Gamma cover rate
```{r}
(cover_rate_temp = Reduce("+", GMN_cover)/length(GMN_cover))
```

Gamma cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(GMN_cover))
```

Alpha bias
```{r}
Reduce("+", AMN_list)/length(AMN_list)-check_para$Alpha
```

Alpha sd
```{r}
sqrt(
  Reduce("+", lapply(AMN_list, "^", 2)) / length(AMN_list) - 
       (Reduce("+", AMN_list)/length(AMN_list))^2
  )
```


Alpha cover rate
```{r}
(cover_rate_temp = Reduce("+", AMN_cover)/length(AMN_cover))
```

Alpha cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(AMN_cover))
```

Thres bias
```{r}
Reduce("+", thres_list)/length(thres_list)-check_para$thres
```

Thres sd
```{r}
sqrt(
  Reduce("+", lapply(thres_list, "^", 2)) / length(thres_list) - 
       (Reduce("+", thres_list)/length(thres_list))^2
  )
```

Thres cover rate
```{r}
(cover_rate_temp = Reduce("+", thres_cover)/length(thres_cover))
```

Thres cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(thres_cover))
```

Global random effect variance bias
```{r}
mean(unlist(sigma_delta_sq_mean_list))-check_para$sigma_b_delta^2
```
Global random effect variance sd
```{r}
sqrt(
  Reduce("+", lapply(sigma_delta_sq_mean_list, "^", 2)) / length(sigma_delta_sq_mean_list) - 
       (Reduce("+", sigma_delta_sq_mean_list)/length(sigma_delta_sq_mean_list))^2
  )
```
Global random effect variance coverage rate
```{r}
(cover_rate_temp = mean(unlist(sigma_delta_sq_cover)))
```

Global random effect cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(sigma_delta_sq_cover))
```

Local random effect variance bias
```{r}
mean(unlist(Sigma_eta_mean_list))-check_para$Sigma_b_eta^2
```

Local random effect variance sd
```{r}
sqrt(
  Reduce("+", lapply(Sigma_eta_mean_list, "^", 2)) / length(Sigma_eta_mean_list) - 
       (Reduce("+", Sigma_eta_mean_list)/length(Sigma_eta_mean_list))^2
  )
```

Local random effect variance coverage rate
```{r}
(cover_rate_temp = mean(unlist(Sigma_eta_cover)))
```

Local random effect cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(Sigma_eta_cover))
```

# Result table
True parameters
```{r}
check_para
```

```{r}
# Cover rate
covar_mean_cover = Reduce("+", mean_cover)/length(mean_cover)
covar_median_cover = Reduce("+", median_cover)/length(median_cover)
covar_0.75_cover = Reduce("+", perc.75_cover)/length(perc.75_cover)
dist_name = c("mean", "median",  "perc.25",  "perc.75")
dist_cover1 = Reduce("+", dist_cover)/length(dist_cover)
sigma_b_delta_cover = mean(unlist(sigma_delta_sq_cover))
sigma_b_eta_cover = mean(unlist(Sigma_eta_cover))

# Mean 
covar_mean = Reduce("+", mean_list)/length(mean_list)
covar_median = Reduce("+", median_list)/length(median_list)
covar_0.75 = Reduce("+", perc.75_list)/length(perc.75_list)
dist = Reduce("+", dist_list)/length(dist_list)
sigma_b_delta_mean = mean(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_mean = mean(unlist(Sigma_eta_mean_list))
# Variance 
covar_mean_sd = apply(simplify2array(mean_list), 1:2, sd)
covar_median_sd = apply(simplify2array(median_list), 1:2, sd)
covar_0.75_sd = apply(simplify2array(perc.75_list), 1:2, sd)
dist_sd = apply(simplify2array(dist_list), 1:2, sd)
sigma_b_delta_sd = sd(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_sd = sqrt(
  Reduce("+", lapply(Sigma_eta_mean_list, "^", 2)) / length(Sigma_eta_mean_list) - 
       (Reduce("+", Sigma_eta_mean_list)/length(Sigma_eta_mean_list))^2
  )
  
# True value
covar_mean_true = check_para$effect_mean
covar_median_true = check_para$effect_median
covar_0.75_true = check_para$effect_0.75
dist_true = check_para$effect_dist
sigma_b_delta_true = check_para$sigma_b_delta^2
sigma_b_eta_true = check_para$Sigma_b_eta^2
# Bias
covar_mean_bias = covar_mean-covar_mean_true
covar_median_bias =covar_median - covar_median_true
covar_0.75_bias = covar_0.75 - covar_0.75_true
dist_bias = dist - dist_true
sigma_b_delta_bias = sigma_b_delta_mean-sigma_b_delta_true
sigma_b_eta_bias = sigma_b_eta_mean-sigma_b_eta_true
# Building the table
d = data.frame(names = c(paste(rep("mean",3), c("intercept", "X1", "X2")),
                     paste(rep("median",3), c("intercept", "X1", "X2")),
                     paste(rep("0.75",3), c("intercept", "X1", "X2"))),
           bias = c(covar_mean_bias,covar_median_bias, 
                    covar_0.75_bias),
           sd = c(covar_mean_sd,covar_median_sd,
                  covar_0.75_sd),
           coverage_probability = c(
             covar_mean_cover,covar_median_cover, 
             covar_0.75_cover
           ),
           True_value = c(
             covar_mean_true,covar_median_true,
             covar_0.75_true
           ),
           mean = c(
             covar_mean,covar_median,
             covar_0.75
           )) %>% 
  mutate(MSE = bias^2+sd^2,MC_se = sqrt(coverage_probability * (1-coverage_probability)/length_after))
knitr::kable(d)
if(write_dat){
  write.csv(d, file = table_name)
}
```