---
title: "gen_data_b_spline"
author: "Junting Ren"
date: "11/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(splines)
library(MASS)
library(tidyverse)
library(doParallel) # for parallel computing
library(gridExtra)
library(grid)
library(matrixStats)
source("../../functions/sim_fcns_probit.R")
```


# Generating from our model

Basic hyper parameters to input
```{r}
write_dat =T
read_data = T
# Number of simulation
n_data =500
# Number of b-spline density
K =10
# Number of observations
n = 2000
# Number of time points for each observations
J = 1
# data name
dat_name = paste("./data_b_spline/","b_spline_n_data=",n_data, "_n=", n, ".csv",sep = "")
if(J ==1){
  sigma_b_delta = 0
  sigma_b_eta = 0
}else{
  sigma_b_delta = 1.1#1.1
  sigma_b_eta = 2#2
}
sigma_b = diag(c(sigma_b_eta^2,sigma_b_delta^2), nrow = 2)
# Parameters for prior prob
gamma = c(1,1.2,-1)
# Parameters for K=5 density spline
thres = c(0,0.1,0.15,0.2, 0.22,0.25,0.3,1,1.5)
#Alpha = c(-1,2,-2.5)
#Alpha = c(-1,1,-1)
Alpha = c(0.3,1,-0.5)
```
The Bsplines we are simulating from
```{r}
byStep=0.01
end = 10
grid=seq(byStep,end+byStep,by=byStep)
phi.mat = Bdensity_sim(K = K,byStep = byStep,end = end, degree=3)
draw_b_spline(phi.mat, byStep = byStep, end = end)
```

```{r}
set.seed(2021)
if(read_data){
  data_out = read_csv(dat_name)
}else{
  data_out = data.frame()
  for(i in 1:n_data){
    list_simdata = sim_data_probit(n, J, gamma, Alpha, sigma_b, phi.mat, 
                                   x_type = c("numeric","binary"), 
                                   byStep = byStep, K =K, thres = thres)
    
    
    # subject_gone = sample(1:n, 5) #get rid of 5 subjects
    # b_delta = b_delta[-subject_gone]
    # b_eta = b_eta[-subject_gone,]
    # keep_ind = !(X[,length(gamma)+1] %in% subject_gone)
    # X = X[keep_ind,]
    # Z = Z[keep_ind]
    # subject_with_1_obs = sample(unique(X[,length(gamma)+1]), 10) #10 subjects with 1 observation
    # for(i in subject_with_1_obs){
    #   ind_gone = which((X[,length(gamma)+1] == i))[2:J]
    #   X = X[-ind_gone,]
    #   Z = Z[-ind_gone]
    # }
    
    Z = list_simdata$Z
    G = list_simdata$G
    X = list_simdata$X
    if(J==1){
      data_single = cbind(Z=Z, X, data_set = i)
      colnames(data_single)=c("Z", "x0", "x1", "x2","num")
    }else{
      data_single = cbind(Z=Z, X, G, data_set = i)
      colnames(data_single)=c("Z", "x0", "x1", "x2", "G", "num")
    }
    data_out = rbind(data_out, data_single)
  }
  
}


(true_effect = coeff_effect_probit(quantity = NULL, Alpha, gamma, phi.mat, grid, byStep,K =K, thres = thres))
(dist_effect = unlist(cal_quantity_probit(quantity = NULL,x = rep(1, length(gamma)), Alpha, gamma, phi.mat, grid, byStep, K, thres = thres)))
if(write_dat){
  write.csv(data_out, file = dat_name)
}
```

```{r}
hist(data_out$Z)
```
```{r}
dat_test  = data_out %>% filter(num==9) 
Z = dat_test$Z
X = data.matrix(dplyr::select(dat_test, x0,x1,x2))
hist(Z)
```


```{r}
K_model=K
G = NULL
nIter = 2000
burnIn = 1000
thin = 1
byStep = 0.01
useCov = T
repara_lambda = F
specify_knot = F
internal_knots = NULL
intercept = T
step_thres = 0.02
s_theta = 2 
gamma_prior_var  = 2.5
alpha_prior_var = 100
source("../../functions/Bayesian_Semi_probit.R") #B-spline with intercept
source("../../functions/output_fcns_probit.R")
source("../../functions/sim_fcns_probit.R")
source("../../functions/fcns_rf_probit.R")
source("../../functions/Bdensity.R")
MCMCfit1<-Bayesian_Semi_probit(Z,X,G,K=K_model,nIter,burnIn,thin, useCov=useCov,  byStep=byStep,max_Z = end,c = 0.01, d = 0.01, alpha_prior_var = alpha_prior_var, gamma_prior_var=gamma_prior_var, step_thres = step_thres, repara_lambda = repara_lambda,specify_knot = specify_knot, s_theta = s_theta, internal_knots = internal_knots )

```

```{r}
source("../../functions/output_fcns_probit.R")
draw_b_spline(MCMCfit1)
```


```{r}
MCMCfit = MCMCfit1
convergence_plot_probit(MCMCfit, save=F) 
```

```{r}
last_n = 1000
# True parameters
true_para = true_effect
#Print out the table
(parameter_est = meanCI_probit(MCMCfit1,level = 0.05,true_para = true_para,last_n = last_n, return_all = F ))
```

# The simulation using B-spline model
```{r}
# Cores
cl <- makeCluster(detectCores()-1)
folder_path = "./result_b_spline/"
dat_name = paste(folder_path, "B_spline_data_model", "n=",n,"_","K_model = ",K_model ,"_", Sys.Date(), ".RData", sep = "")
table_name = paste(folder_path, "table_B_spline_data_model", "n=",n,"_", "K_model = ",K_model ,"_", Sys.Date(), ".csv", sep = "")
```

Simualtion html name
```{r}
paste("B_spline_data_model", "n=",n,"_", "K_model = ",K_model ,"_",Sys.Date(), sep = "")
```

```{r}
check_para = list(Alpha = NULL, Gamma = NULL,
                  effect_mean = true_effect$effect_mean, 
                  effect_median = true_effect$effect_median,
                  effect_0.25 = 0,
                  effect_0.75 = true_effect$effect_0.75,
                  effect_dist = 0)
registerDoParallel(cl)
cover_list_list = foreach(t=1:n_data,
                          .errorhandling = "pass", 
                          .inorder = F,.verbose	=T) %dopar% {
                            list_simdata = data_out[data_out$num==t,]
                            Z = list_simdata$Z
                            G = list_simdata$G
                            X = list_simdata[,c("x0", "x1", "x2")]
                            X=data.matrix(X)
                            N=length(Z)
                            Bayesian_Semi_probit(Z,X,G,K=K_model,nIter,burnIn,thin, useCov=useCov,  byStep=byStep,max_Z = end,c = 0.01, d = 0.01, alpha_prior_var = alpha_prior_var, gamma_prior_var=gamma_prior_var, step_thres = step_thres, repara_lambda = repara_lambda,specify_knot = specify_knot, s_theta = s_theta, check_para = check_para, internal_knots = internal_knots, intercept = intercept )
                          }

GMN_list = lapply(cover_list_list,function(x)x$GMN)
AMN_list = lapply(cover_list_list,function(x)x$AMN)
thres_list = lapply(cover_list_list,function(x)x$thres_mean)
mean_list = lapply(cover_list_list,function(x)x$effect_mean)
median_list = lapply(cover_list_list,function(x)x$effect_median)
perc.25_list = lapply(cover_list_list,function(x)x$effect_0.25)
perc.75_list = lapply(cover_list_list,function(x)x$effect_0.75)
dist_list = lapply(cover_list_list,function(x)x$effect_dist)
AMN_cover = lapply(cover_list_list,function(x)x$cover_alpha)
thres_cover = lapply(cover_list_list,function(x)x$cover_thres)
GMN_cover = lapply(cover_list_list,function(x)x$cover_gamma)
mean_cover = lapply(cover_list_list,function(x)x$cover_mean)
median_cover = lapply(cover_list_list,function(x)x$cover_median)
perc.25_cover = lapply(cover_list_list,function(x)x$cover_0.25)
perc.75_cover = lapply(cover_list_list,function(x)x$cover_0.75)
dist_cover = lapply(cover_list_list,function(x)x$cover_dist)
sigma_delta_sq_mean_list = lapply(cover_list_list,function(x)x$sigma_delta_sq_mean)
sigma_delta_sq_cover = lapply(cover_list_list,function(x)x$cover_sigma_delta_sq)
Sigma_eta_mean_list = lapply(cover_list_list,function(x)x$Sigma_eta_mean)
Sigma_eta_cover= lapply(cover_list_list,function(x)x$cover_Sigma_eta)

length_before = length(mean_cover)
if(write_dat){
  save.image(file=dat_name)
}
```

Filter out the null simulations
```{r}
GMN_list = Filter(Negate(is.null), GMN_list)
AMN_list = Filter(Negate(is.null), AMN_list)
thres_list = Filter(Negate(is.null), thres_list)
AMN_cover = Filter(Negate(is.null), AMN_cover)
thres_cover = Filter(Negate(is.null), thres_cover)
GMN_cover = Filter(Negate(is.null), GMN_cover)
mean_list = Filter(Negate(is.null), mean_list)
median_list = Filter(Negate(is.null), median_list)
perc.25_list = Filter(Negate(is.null), perc.25_list)
perc.75_list = Filter(Negate(is.null), perc.75_list)
dist_list = Filter(Negate(is.null), dist_list)
mean_cover = Filter(Negate(is.null), mean_cover)
median_cover = Filter(Negate(is.null), median_cover)
perc.25_cover = Filter(Negate(is.null), perc.25_cover)
perc.75_cover = Filter(Negate(is.null), perc.75_cover)
dist_cover = Filter(Negate(is.null), dist_cover)
sigma_delta_sq_mean_list = Filter(Negate(is.null), sigma_delta_sq_mean_list)
sigma_delta_sq_cover = Filter(Negate(is.null), sigma_delta_sq_cover)
Sigma_eta_mean_list = Filter(Negate(is.null), Sigma_eta_mean_list)
Sigma_eta_cover = Filter(Negate(is.null), Sigma_eta_cover)

length_after =  length(perc.75_cover)
print("# of simulation filter out")
length_before - length_after
```

```{r}
#Cover rate
print("Global mean cover rate")
Reduce("+", mean_cover)/length(mean_cover)
print("Global median cover rate")
Reduce("+", median_cover)/length(median_cover)
print("Global 0.25 perc cover rate")
Reduce("+", perc.25_cover)/length(perc.25_cover)
print("Global 0.75 perc cover rate")
Reduce("+", perc.75_cover)/length(perc.75_cover)
print("Distribution quantity cover rate:  mean   median  perc.25  perc.75 ")
Reduce("+", dist_cover)/length(dist_cover)
print("Alpha cover rate")
Reduce("+", AMN_cover)/length(AMN_cover)
print("Thres cover rate")
Reduce("+", thres_cover)/length(thres_cover)
print("Gamma cover rate")
Reduce("+", GMN_cover)/length(GMN_cover)

#Mean
print("Global mean")
Reduce("+", mean_list)/length(mean_list)
print("Global mean true")
check_para$effect_mean

print("Global median")
Reduce("+", median_list)/length(median_list)
print("Global median true")
check_para$effect_median

print("Global perc 0.25")
Reduce("+", perc.25_list)/length(perc.25_list)
print("Global prec 0.25 true")
check_para$effect_0.25

print("Global perc 0.75")
Reduce("+", perc.75_list)/length(perc.75_list)
print("Global 0.75 true")
check_para$effect_0.75
print("Dist quantity mean")
Reduce("+", dist_list)/length(dist_list)
print("Distribution quantity true")
check_para$effect_dist

print("Alpha mean")
Reduce("+", AMN_list)/length(AMN_list)
print("True Alpha")
check_para$Alpha
print("Thres mean")
Reduce("+", thres_list)/length(thres_list)
print("True thres")
check_para$thres
print("Gamma mean")
Reduce("+", GMN_list)/length(GMN_list)
print("True Gamma")
check_para$Gamma
print("Sigma_delta_sq cover rate")
mean(unlist(sigma_delta_sq_cover))
print("Mean Sigma_delta_sq_mean")
mean(unlist(sigma_delta_sq_mean_list))
print("true Sigma_delta_sq")
check_para$sigma_b_delta^2
print("Simga_eta cover rate")
mean(unlist(Sigma_eta_cover))
print("Mean Simga_eta_mean")
mean(unlist(Sigma_eta_mean_list))
print("true Sigma_eta_square")
check_para$Sigma_b_eta^2
```

Gamma bias
```{r}
Reduce("+", GMN_list)/length(GMN_list)-check_para$Gamma
```

Gamma sd
```{r}
sqrt(
  Reduce("+", lapply(GMN_list, "^", 2)) / length(GMN_list) - 
       (Reduce("+", GMN_list)/length(GMN_list))^2
  )
```

Gamma cover rate
```{r}
(cover_rate_temp = Reduce("+", GMN_cover)/length(GMN_cover))
```

Gamma cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(GMN_cover))
```

Alpha bias
```{r}
Reduce("+", AMN_list)/length(AMN_list)-check_para$Alpha
```

Alpha sd
```{r}
sqrt(
  Reduce("+", lapply(AMN_list, "^", 2)) / length(AMN_list) - 
       (Reduce("+", AMN_list)/length(AMN_list))^2
  )
```


Alpha cover rate
```{r}
(cover_rate_temp = Reduce("+", AMN_cover)/length(AMN_cover))
```

Alpha cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(AMN_cover))
```

Thres bias
```{r}
Reduce("+", thres_list)/length(thres_list)-check_para$thres
```

Thres sd
```{r}
sqrt(
  Reduce("+", lapply(thres_list, "^", 2)) / length(thres_list) - 
       (Reduce("+", thres_list)/length(thres_list))^2
  )
```

Thres cover rate
```{r}
(cover_rate_temp = Reduce("+", thres_cover)/length(thres_cover))
```

Thres cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(thres_cover))
```

Global random effect variance bias
```{r}
mean(unlist(sigma_delta_sq_mean_list))-check_para$sigma_b_delta^2
```
Global random effect variance sd
```{r}
sqrt(
  Reduce("+", lapply(sigma_delta_sq_mean_list, "^", 2)) / length(sigma_delta_sq_mean_list) - 
       (Reduce("+", sigma_delta_sq_mean_list)/length(sigma_delta_sq_mean_list))^2
  )
```
Global random effect variance coverage rate
```{r}
(cover_rate_temp = mean(unlist(sigma_delta_sq_cover)))
```

Global random effect cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(sigma_delta_sq_cover))
```

Local random effect variance bias
```{r}
mean(unlist(Sigma_eta_mean_list))-check_para$Sigma_b_eta^2
```

Local random effect variance sd
```{r}
sqrt(
  Reduce("+", lapply(Sigma_eta_mean_list, "^", 2)) / length(Sigma_eta_mean_list) - 
       (Reduce("+", Sigma_eta_mean_list)/length(Sigma_eta_mean_list))^2
  )
```

Local random effect variance coverage rate
```{r}
(cover_rate_temp = mean(unlist(Sigma_eta_cover)))
```

Local random effect cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(Sigma_eta_cover))
```

# Result table
True parameters
```{r}
check_para
```

```{r}
# Cover rate
covar_mean_cover = Reduce("+", mean_cover)/length(mean_cover)
covar_median_cover = Reduce("+", median_cover)/length(median_cover)
covar_0.75_cover = Reduce("+", perc.75_cover)/length(perc.75_cover)
dist_name = c("mean", "median",  "perc.25",  "perc.75")
dist_cover1 = Reduce("+", dist_cover)/length(dist_cover)
sigma_b_delta_cover = mean(unlist(sigma_delta_sq_cover))
sigma_b_eta_cover = mean(unlist(Sigma_eta_cover))

# Mean 
covar_mean = Reduce("+", mean_list)/length(mean_list)
covar_median = Reduce("+", median_list)/length(median_list)
covar_0.75 = Reduce("+", perc.75_list)/length(perc.75_list)
dist = Reduce("+", dist_list)/length(dist_list)
sigma_b_delta_mean = mean(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_mean = mean(unlist(Sigma_eta_mean_list))
# Variance 
covar_mean_sd = apply(simplify2array(mean_list), 1:2, sd)
covar_median_sd = apply(simplify2array(median_list), 1:2, sd)
covar_0.75_sd = apply(simplify2array(perc.75_list), 1:2, sd)
dist_sd = apply(simplify2array(dist_list), 1:2, sd)
sigma_b_delta_sd = sd(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_sd = sqrt(
  Reduce("+", lapply(Sigma_eta_mean_list, "^", 2)) / length(Sigma_eta_mean_list) - 
       (Reduce("+", Sigma_eta_mean_list)/length(Sigma_eta_mean_list))^2
  )
  
# True value
covar_mean_true = check_para$effect_mean
covar_median_true = check_para$effect_median
covar_0.75_true = check_para$effect_0.75
dist_true = check_para$effect_dist
sigma_b_delta_true = check_para$sigma_b_delta^2
sigma_b_eta_true = check_para$Sigma_b_eta^2
# Bias
covar_mean_bias = covar_mean-covar_mean_true
covar_median_bias =covar_median - covar_median_true
covar_0.75_bias = covar_0.75 - covar_0.75_true
dist_bias = dist - dist_true
sigma_b_delta_bias = sigma_b_delta_mean-sigma_b_delta_true
sigma_b_eta_bias = sigma_b_eta_mean-sigma_b_eta_true
# Building the table
d = data.frame(names = c(paste(rep("mean",3), c("intercept", "X1", "X2")),
                     paste(rep("median",3), c("intercept", "X1", "X2")),
                     paste(rep("0.75",3), c("intercept", "X1", "X2"))),
           bias = c(covar_mean_bias,covar_median_bias, 
                    covar_0.75_bias),
           sd = c(covar_mean_sd,covar_median_sd,
                  covar_0.75_sd),
           coverage_probability = c(
             covar_mean_cover,covar_median_cover, 
             covar_0.75_cover
           ),
           True_value = c(
             covar_mean_true,covar_median_true,
             covar_0.75_true
           ),
           mean = c(
             covar_mean,covar_median,
             covar_0.75
           )) %>% 
  mutate(MSE = bias^2+sd^2,MC_se = sqrt(coverage_probability * (1-coverage_probability)/length_after))
knitr::kable(d)
if(write_dat){
  write.csv(d, file = table_name)
}
```