---
title: "Cover rate"
author: "Junting Ren"
date: "1/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(splines)
library(MASS)
library(tidyverse)
library(doParallel) # for parallel computing
source("../functions/output_fcns.R")
source("../functions/sim_fcns.R")
source("../functions/Bayesian_Semi.R") #B-spline with intercept
source("../functions/fcns_rf.R")# This function should be in LFDR_CMBsplines_modified_intercept_rf.R but parallel requires it to be called here
```

The Bsplines we are simulating from
```{r}
byStep=0.01
end = 150
grid=seq(byStep,end+byStep,by=byStep)
phi.mat = Bdensity_sim(K = 5,byStep = byStep,end = end)
draw_b_spline(phi.mat, byStep = byStep, end = end)
```

# Basic hyper parameters to input
```{r}
# Number of b-spline density
K = 5
# Number of observations
n = 2000 
# Number of time points for each observations
J = 1 

#For test run, take smaller iterations.
thin=1;
nIter=4000;
burnIn=2000;
useCov=1;


mu=0;
initNULL=0.5;


```


# Simulate data: with prob on 1st 
```{r}
start_time <- Sys.time()
sim_num = 5
one_obs =F # whether to make some subjects with one observation
# simulate data
sigma_b_delta = 0#1.1
sigma_b_eta = 0#2
sigma_b = diag(c(rep(sigma_b_eta^2,K-1),sigma_b_delta^2), nrow = K)
# Parameters for prior prob
gamma = c(-1,1.2,1)# intercept and slope
# Parameters for K=5 density spline
alpha1 = c(0,0,0)
alpha2 = c(-3,1.2,0.7)
alpha3 = c(-4,0.2,1)
alpha4 = c(-5,1,1.5)
alpha5 = c(-5,-1,0.4)
Alpha = cbind(alpha1, alpha2,alpha3, alpha4, alpha5)
true_alpha = as.matrix(cbind(alpha1, alpha2, alpha3, alpha4, alpha5))
true_effect = coeff_effect(quantity = NULL, Alpha, gamma, phi.mat, grid, byStep)
dist_effect = unlist(cal_quantity(quantity = NULL,x = rep(1, length(gamma)), Alpha, gamma, phi.mat, grid, byStep))
check_para = list(Alpha = true_alpha, Gamma = gamma, 
                  sigma_b_delta = sigma_b_delta, Sigma_b_eta = sigma_b_eta,
                  effect_mean = true_effect$effect_mean, 
                  effect_median = true_effect$effect_median,
                  effect_0.25 = true_effect$effect_0.25,
                  effect_0.75 = true_effect$effect_0.75,
                  effect_dist = dist_effect)
# Empty list for saving results
GMN_list = list()
AMN_list = list()
global_list = list()
local_list = list()
AMN_cover = list()
GMN_cover = list()
global_cover = list()
local_cover = list()
sigma_delta_sq_mean_list = list()
sigma_delta_sq_cover = list()
Sigma_eta_mean_list = list()
Sigma_eta_cover = list()

list_simdata_list = list()
for(t in 1: sim_num){
  list_simdata_list[[t]] = sim_data(n, J, gamma, Alpha, sigma_b, phi.mat, 
                                    x_type = c("numeric","binary"), 
                                    byStep = byStep)
}
```

```{r}
cl <- makeCluster(detectCores(),outfile="Log.txt")
registerDoParallel(cl)
cover_list_list = foreach(t=1:sim_num,
                          .errorhandling = "pass", 
                          .inorder = F,.verbose	=T) %dopar% {
  list_simdata = list_simdata_list[[t]]
  Z = list_simdata$Z
  G = list_simdata$G
  X = list_simdata$X
  if(one_obs){
    subject_with_1_obs = sample(unique(X[,length(gamma)+1]), 10) #10 subjects with 1 observation
    for(i in subject_with_1_obs){
      ind_gone = which((X[,length(gamma)+1] == i))[2:J]
      X = X[-ind_gone,]
      G = G[-ind_gone,]
      Z = Z[-ind_gone]
    }
  }
  X=data.matrix(X)
  N=length(Z)
  if(useCov==1){
    M=dim(X)[2]; #M: number of the covariates including intercept
    SSA=c(5,rep(5,M-1)) #change step-size for alpha draw; length(SSA)=M 
    SSAP=rep(0.8,M); # prob that step-size of alpha will be changed to SSA; length(SSAP)=M;
    MA=rep(5,M); #num of multiple try for alpha; length(MA)=M;
  }else{
    M=1;
    SSA=20;SSAP=0.4;MA=5;
  }
  SSG=1# change step-size for gamma draw
  MG=3 #num of multiple try for gamma
  if(M > 3){
    s_alpha = c(0.1, rep(0.1, M-2), 0.1)
  }else{
    s_alpha = c(0.2, rep(0.15, M-1))
  }
  #true_para = list(Sigma_b_eta = diag(sigma_b_eta^2, K-1), sigma_b_delta_sq = sigma_b_delta^2, b_eta = list_simdata$b_eta, Alpha = true_alpha), if they are in the list, then their value is fixed at the true value
  Bayesian_Semi(Z,X,G,K,nIter,burnIn,thin, useCov=useCov,  byStep=byStep, same_b_eta_variance = T,max_Z = end,s_b_eta = 2, c = 0.01, d = 0.01, alpha_prior_var = 2.5, gamma_prior_var=2.5, same_var = F, check_para = check_para)
}
end_time <- Sys.time()

GMN_list = lapply(cover_list_list,function(x)x$GMN)
AMN_list = lapply(cover_list_list,function(x)x$AMN)
mean_list = lapply(cover_list_list,function(x)x$effect_mean)
median_list = lapply(cover_list_list,function(x)x$effect_median)
perc.25_list = lapply(cover_list_list,function(x)x$effect_0.25)
perc.75_list = lapply(cover_list_list,function(x)x$effect_0.75)
dist_list = lapply(cover_list_list,function(x)x$effect_dist)
AMN_cover = lapply(cover_list_list,function(x)x$cover_alpha)
GMN_cover = lapply(cover_list_list,function(x)x$cover_gamma)
mean_cover = lapply(cover_list_list,function(x)x$cover_mean)
median_cover = lapply(cover_list_list,function(x)x$cover_median)
perc.25_cover = lapply(cover_list_list,function(x)x$cover_0.25)
perc.75_cover = lapply(cover_list_list,function(x)x$cover_0.75)
dist_cover = lapply(cover_list_list,function(x)x$cover_dist)
sigma_delta_sq_mean_list = lapply(cover_list_list,function(x)x$sigma_delta_sq_mean)
sigma_delta_sq_cover = lapply(cover_list_list,function(x)x$cover_sigma_delta_sq)
Sigma_eta_mean_list = lapply(cover_list_list,function(x)x$Sigma_eta_mean)
Sigma_eta_cover= lapply(cover_list_list,function(x)x$cover_Sigma_eta)
save(file="cover_rate_result_temp.R",GMN_list,AMN_list,AMN_cover,
     GMN_cover,mean_list,median_list,perc.25_list, perc.75_list,dist_list,
     mean_cover,median_cover,perc.25_cover,perc.75_cover,dist_cover,
     sigma_delta_sq_mean_list,sigma_delta_sq_cover,Sigma_eta_mean_list,Sigma_eta_cover,
     check_para,end)

GMN_list = Filter(Negate(is.null), GMN_list)
AMN_list = Filter(Negate(is.null), AMN_list)
AMN_cover = Filter(Negate(is.null), AMN_cover)
GMN_cover = Filter(Negate(is.null), GMN_cover)
mean_list = Filter(Negate(is.null), mean_list)
median_list = Filter(Negate(is.null), median_list)
perc.25_list = Filter(Negate(is.null), perc.25_list)
perc.75_list = Filter(Negate(is.null), perc.75_list)
dist_list = Filter(Negate(is.null), dist_list)
mean_cover = Filter(Negate(is.null), mean_cover)
median_cover = Filter(Negate(is.null), median_cover)
perc.25_cover = Filter(Negate(is.null), perc.25_cover)
perc.75_cover = Filter(Negate(is.null), perc.75_cover)
dist_cover = Filter(Negate(is.null), dist_cover)
sigma_delta_sq_mean_list = Filter(Negate(is.null), sigma_delta_sq_mean_list)
sigma_delta_sq_cover = Filter(Negate(is.null), sigma_delta_sq_cover)
Sigma_eta_mean_list = Filter(Negate(is.null), Sigma_eta_mean_list)
Sigma_eta_cover = Filter(Negate(is.null), Sigma_eta_cover)

# Check if sigma_eta is too large (not converging)
indx_conv = sapply(Sigma_eta_mean_list, function(x) x[1,1])<20
GMN_list = GMN_list[indx_conv]
AMN_list = AMN_list[indx_conv]
AMN_cover = AMN_cover[indx_conv]
GMN_cover = GMN_cover[indx_conv]
mean_list = mean_list[indx_conv]
median_list = median_list[indx_conv]
perc.25_list = perc.25_list[indx_conv]
perc.75_list = perc.75_list[indx_conv]
dist_list = dist_list[indx_conv]
mean_cover = mean_cover[indx_conv]
median_cover = median_cover[indx_conv]
perc.25_cover = perc.25_cover[indx_conv]
perc.75_cover = perc.75_cover[indx_conv]
dist_cover = dist_cover[indx_conv]
sigma_delta_sq_mean_list = sigma_delta_sq_mean_list[indx_conv]
sigma_delta_sq_cover = sigma_delta_sq_cover[indx_conv]
Sigma_eta_mean_list = Sigma_eta_mean_list[indx_conv]
Sigma_eta_cover = Sigma_eta_cover[indx_conv]
```


```{r}
#Cover rate
print("Global mean cover rate")
Reduce("+", mean_cover)/length(mean_cover)
print("Global median cover rate")
Reduce("+", median_cover)/length(median_cover)
print("Global 0.25 perc cover rate")
Reduce("+", perc.25_cover)/length(perc.25_cover)
print("Global 0.75 perc cover rate")
Reduce("+", perc.75_cover)/length(perc.75_cover)
print("Distribution quantity cover rate:  mean   median  perc.25  perc.75 ")
Reduce("+", dist_cover)/length(dist_cover)
print("Alpha cover rate")
apply(simplify2array(AMN_cover), 1:2, mean)
print("Gamma cover rate")
Reduce("+", GMN_cover)/length(GMN_cover)

#Mean
print("Global mean")
Reduce("+", mean_list)/length(mean_list)
print("Global mean true")
check_para$effect_mean

print("Global median")
Reduce("+", median_list)/length(median_list)
print("Global median true")
check_para$effect_median

print("Global perc 0.25")
Reduce("+", perc.25_list)/length(perc.25_list)
print("Global mean true")
check_para$effect_0.25

print("Global perc 0.75")
Reduce("+", perc.75_list)/length(perc.75_list)
print("Global 0.75 true")
check_para$effect_0.75
print("Dist quantity mean")
Reduce("+", dist_list)/length(dist_list)
print("Distribution quantity true")
check_para$effect_dist

print("Alpha mean")
t(apply(simplify2array(AMN_list), 1:2, mean))
print("True Alpha")
check_para$Alpha
print("Gamma mean")
Reduce("+", GMN_list)/length(GMN_list)
print("True Gamma")
check_para$Gamma
print("Sigma_delta_sq cover rate")
mean(unlist(sigma_delta_sq_cover))
print("Mean Sigma_delta_sq_mean")
mean(unlist(sigma_delta_sq_mean_list))
print("true Sigma_delta_sq")
check_para$sigma_b_delta^2
print("Simga_eta cover rate")
apply(simplify2array(Sigma_eta_cover), 1:2, mean)
print("Mean Simga_eta_mean")
apply(simplify2array(Sigma_eta_mean_list), 1:2, mean)
print("true Sigma_eta_square")
check_para$Sigma_b_eta^2
```

# Time consumed
```{r}
end_time - start_time
```

# Supplement material table
# ```{r}
# load("./cover_rate_result_temp_n=40_J=100.R")
# ```

Gamma bias
```{r}
Reduce("+", GMN_list)/length(GMN_list)-check_para$Gamma
```

Gamma cover rate
```{r}
Reduce("+", GMN_cover)/length(GMN_cover)
```

Alpha bias
```{r}
t(apply(simplify2array(AMN_list), 1:2, mean)) -check_para$Alpha
```

Alpha cover rate
```{r}
print("Alpha cover rate")
apply(simplify2array(AMN_cover), 1:2, mean)
```

Global random effect variance bias
```{r}
mean(unlist(sigma_delta_sq_mean_list))-check_para$sigma_b_delta^2
```

Global random effect variance coverage rate
```{r}
mean(unlist(sigma_delta_sq_cover))
```

Local random effect variance bias
```{r}
apply(simplify2array(Sigma_eta_mean_list), 1:2, mean)-check_para$Sigma_b_eta^2
```

Local random effect variance coverage rate
```{r}
apply(simplify2array(Sigma_eta_cover), 1:2, mean)
```


# Result table
True parameters
```{r}
check_para
```

```{r}
# Cover rate
covar_mean_cover = Reduce("+", mean_cover)/length(mean_cover)
covar_median_cover = Reduce("+", median_cover)/length(median_cover)
covar_0.75_cover = Reduce("+", perc.75_cover)/length(perc.75_cover)
dist_name = c("mean", "median",  "perc.25",  "perc.75")
dist_cover1 = Reduce("+", dist_cover)/length(dist_cover)
sigma_b_delta_cover = mean(unlist(sigma_delta_sq_cover))
sigma_b_eta_cover = apply(simplify2array(Sigma_eta_cover), 1:2, mean)[1,1]

# Mean 
covar_mean = Reduce("+", mean_list)/length(mean_list)
covar_median = Reduce("+", median_list)/length(median_list)
covar_0.75 = Reduce("+", perc.75_list)/length(perc.75_list)
dist = Reduce("+", dist_list)/length(dist_list)
sigma_b_delta_mean = mean(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_mean = apply(simplify2array(Sigma_eta_mean_list), 1:2, mean)[1,1]
# Variance 
covar_mean_sd = apply(simplify2array(mean_list), 1:2, sd)
covar_median_sd = apply(simplify2array(median_list), 1:2, sd)
covar_0.75_sd = apply(simplify2array(perc.75_list), 1:2, sd)
dist_sd = apply(simplify2array(dist_list), 1:2, sd)
sigma_b_delta_sd = sd(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_sd = apply(simplify2array(Sigma_eta_mean_list), 1:2, sd)[1,1]
# True value
covar_mean_true = check_para$effect_mean
covar_median_true = check_para$effect_median
covar_0.75_true = check_para$effect_0.75
dist_true = check_para$effect_dist
sigma_b_delta_true = check_para$sigma_b_delta^2
sigma_b_eta_true = check_para$Sigma_b_eta^2
# Bias
covar_mean_bias = covar_mean-covar_mean_true
covar_median_bias =covar_median - covar_median_true
covar_0.75_bias = covar_0.75 - covar_0.75_true
dist_bias = dist - dist_true
sigma_b_delta_bias = sigma_b_delta_mean-sigma_b_delta_true
sigma_b_eta_bias = sigma_b_eta_mean-sigma_b_eta_true
# Building the table
d = data.frame(names = c(paste(rep("mean",3), c("intercept", "X1", "X2")),
                     paste(rep("median",3), c("intercept", "X1", "X2")),
                     paste(rep("0.75",3), c("intercept", "X1", "X2")),
                     paste(rep("distribution", 4), dist_name),
                     "sigma_b_delta", "sigma_b_eta"
                     ),
           bias = c(covar_mean_bias, covar_median_bias, 
                    covar_0.75_bias,dist_bias,sigma_b_delta_bias,sigma_b_eta_bias
                    ),
           sd = c(covar_mean_sd, covar_median_sd,
                  covar_0.75_sd, dist_sd, sigma_b_delta_sd,sigma_b_eta_sd
                  ),
           coverage_probability = c(
             covar_mean_cover, covar_median_cover, 
             covar_0.75_cover,dist_cover1, sigma_b_delta_cover,sigma_b_eta_cover
           ),
           True_value = c(
             covar_mean_true,covar_median_true,
             covar_0.75_true,dist_true, sigma_b_delta_true,sigma_b_eta_true
           ),
           mean = c(
             covar_mean,covar_median,
             covar_0.75, dist, sigma_b_delta_mean, sigma_b_eta_mean
           ))
d
write.csv(d, file = "temp_table.csv")
```


