---
title: "Spline misspecification"
author: "Junting Ren"
date: "1/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(splines)
library(MASS)
library(tidyverse)
library(doParallel) # for parallel computing
source("../functions/output_fcns_probit.R")
source("../functions/sim_fcns_probit.R")
source("../functions/Bayesian_Semi_probit.R") #B-spline with intercept
source("../functions/fcns_rf_probit.R")# This function should be in LFDR_CMBsplines_modified_intercept_rf.R but parallel requires it to be called here
```

# Basic hyper parameters to input
```{r}
# Number of b-spline density for simulation
K = 5
# Number of b-spline dnesity for the actual model
K_model = 10
# Number of observations
n = 100
# whether to sepcify the knots
specify_knot = F
# Whehter to reparametric the thresholds
repara_lambda = F
# Number of time points for each observations
J = 10 
#number of simulations
sim_num = 500
#For test run, take smaller iterations.
thin=1;
nIter=2000;
burnIn=1000;
useCov=1;
# Variance
if(J ==1){
  sigma_b_delta = 0
  sigma_b_eta = 0
  sigma_b = diag(c(sigma_b_eta^2,sigma_b_delta^2), nrow = 2)
  cor = 0
}else{
  sigma_b_delta = 1.1#1.1
  sigma_b_eta = 2 #2
  cor = 0.2
  sigma_b = diag(c(sigma_b_eta^2,sigma_b_delta^2), nrow = 2)
  sigma_b[1,2] = cor *sqrt(sigma_b_delta)*sqrt(sigma_b_eta)
  sigma_b[2,1] = cor *sqrt(sigma_b_delta)*sqrt(sigma_b_eta)
}

# Coefficient parameters
gamma = c(-1,1.2,1)# intercept and slope
# Parameters for K=5 density spline
#Alpha = c(-1,0.35,0.6)
Alpha = c(-1,1.8,1.6)
thres = c(0,1.9,3,3.5)  

# Cores
cl <- makeCluster(detectCores()-1)
# mu=0;
# initNULL=0.5;
write_dat = T
folder_path = "./saved_sim_misspecification/"
if(specify_knot){
  dat_name = paste(folder_path, "missspec_","n=",n,"_", "K=",K,"_", "K_model=",K_model,"_","J=", J, "_","specify_knot","_",Sys.Date(), ".R", sep = "")
  table_name = paste(folder_path, "table_missspec", "n=",n,"_", "K=",K,"_","J=", J, "_", "K_model=",K_model,"_","J=", J, "_","specify_knot","_", Sys.Date(), ".csv", sep = "")
}else{
  dat_name = paste(folder_path, "missspec_","n=",n,"_", "K=",K,"_", "K_model=",K_model,"_","J=", J, "_",Sys.Date(), ".R", sep = "")
  table_name = paste(folder_path, "table_missspec", "n=",n,"_", "K=",K,"_", "K_model=",K_model,"_","J=", J, "_", Sys.Date(), ".csv", sep = "")
}

```


The Bsplines we are simulating from
```{r}
byStep=0.01
end = 150
grid=seq(byStep,end+byStep,by=byStep)
phi.mat = Bdensity_sim(K = K,byStep = byStep,end = end)
draw_b_spline(phi.mat, byStep = byStep, end = end)
```


# Simualtion html name
```{r}
if(specify_knot){
  paste("missspec_","n=",n,"_", "K=",K,"_", "K_model=",K_model,"_","specify_knot","_",Sys.Date(), sep = "")
}else{
  paste("missspec_","n=",n,"_", "K=",K,"_", "K_model=",K_model,"_",Sys.Date(), sep = "")
}

```

# Simulate data: with prob on 1st 
```{r}
start_time <- Sys.time()
one_obs =F # whether to make some subjects with one observation
# simulate data
# Parameters for prior prob
true_effect = coeff_effect_probit(quantity = NULL, Alpha, gamma, phi.mat, grid, byStep,K =K, thres = thres)
dist_effect = unlist(cal_quantity_probit(quantity = NULL,x = rep(1, length(gamma)), Alpha, gamma, phi.mat, grid, byStep, K, thres = thres))
check_para = list(Alpha = Alpha, Gamma = gamma,
                  effect_mean = true_effect$effect_mean, 
                  effect_median = true_effect$effect_median,
                  effect_0.25 = true_effect$effect_0.25,
                  effect_0.75 = true_effect$effect_0.75,
                  effect_dist = dist_effect)
# Empty list for saving results
GMN_list = list()
AMN_list = list()
global_list = list()
local_list = list()
AMN_cover = list()
GMN_cover = list()
global_cover = list()
local_cover = list()
sigma_delta_sq_mean_list = list()
sigma_delta_sq_cover = list()
Sigma_eta_mean_list = list()
Sigma_eta_cover = list()

list_simdata_list = list()
for(t in 1: sim_num){
  list_simdata_list[[t]] = sim_data_probit(n, J, gamma, Alpha, sigma_b, phi.mat, 
                        x_type = c("numeric","binary"), 
                        byStep = byStep, K =K, thres = thres,random_effect_equal = F)
}
```

```{r}
registerDoParallel(cl)
cover_list_list = foreach(t=1:sim_num,
                          .errorhandling = "pass", 
                          .inorder = F,.verbose	=T) %dopar% {
                            list_simdata = list_simdata_list[[t]]
                            Z = list_simdata$Z
                            G = list_simdata$G
                            X = list_simdata$X
                            if(one_obs){
                              subject_with_1_obs = sample(unique(X[,length(gamma)+1]), 10) #10 subjects with 1 observation
                              for(i in subject_with_1_obs){
                                ind_gone = which((X[,length(gamma)+1] == i))[2:J]
                                X = X[-ind_gone,]
                                G = G[-ind_gone,]
                                Z = Z[-ind_gone]
                              }
                            }
                            X=data.matrix(X)
                            N=length(Z)
                            if(useCov==1){
                              M=dim(X)[2]; #M: number of the covariates including intercept
                              SSA=c(5,rep(5,M-1)) #change step-size for alpha draw; length(SSA)=M 
                              SSAP=rep(0.8,M); # prob that step-size of alpha will be changed to SSA; length(SSAP)=M;
                              MA=rep(5,M); #num of multiple try for alpha; length(MA)=M;
                            }else{
                              M=1;
                              SSA=20;SSAP=0.4;MA=5;
                            }
                            SSG=1# change step-size for gamma draw
                            MG=3 #num of multiple try for gamma
                            if(M > 3){
                              s_alpha = c(0.1, rep(0.1, M-2), 0.1)
                            }else{
                              s_alpha = c(0.2, rep(0.15, M-1))
                            }
                            #true_para = list(Sigma_b_eta = diag(sigma_b_eta^2, K-1), sigma_b_delta_sq = sigma_b_delta^2, b_eta = list_simdata$b_eta, Alpha = true_alpha), if they are in the list, then their value is fixed at the true value
                            quantile_z = quantile(Z[Z > 0], probs = 0.99)
                            if(K_model > 8 & specify_knot){
                              internal_knots = c(quantile(
                                Z[Z!=0 & Z<quantile_z],
                                seq(0,1,length.out = (K_model)-ceiling((K_model)*0.2))),
                                seq(quantile_z, end,
                                    length.out = ceiling((K_model)*0.2+1))[-1])
                              internal_knots = internal_knots[-length(internal_knots)]
                              internal_knots = internal_knots[-1]
                            }else{
                              specify_knot = F
                              internal_knots = NULL
                            }
                            options(error = recover)
                            source("../functions/Bdensity.R")
                            Bayesian_Semi_probit(Z,X,G,K=K_model,nIter,burnIn,thin, useCov=useCov,  byStep=byStep,max_Z = end,c = 0.01, d = 0.01, alpha_prior_var = 2.5, gamma_prior_var=2.5,check_para = check_para, internal_knots = internal_knots,
                                                 repara_lambda = repara_lambda)
                          }
end_time <- Sys.time()

GMN_list = lapply(cover_list_list,function(x)x$GMN)
AMN_list = lapply(cover_list_list,function(x)x$AMN)
thres_list = lapply(cover_list_list,function(x)x$thres_mean)
mean_list = lapply(cover_list_list,function(x)x$effect_mean)
median_list = lapply(cover_list_list,function(x)x$effect_median)
perc.25_list = lapply(cover_list_list,function(x)x$effect_0.25)
perc.75_list = lapply(cover_list_list,function(x)x$effect_0.75)
dist_list = lapply(cover_list_list,function(x)x$effect_dist)
AMN_cover = lapply(cover_list_list,function(x)x$cover_alpha)
thres_cover = lapply(cover_list_list,function(x)x$cover_thres)
GMN_cover = lapply(cover_list_list,function(x)x$cover_gamma)
mean_cover = lapply(cover_list_list,function(x)x$cover_mean)
median_cover = lapply(cover_list_list,function(x)x$cover_median)
perc.25_cover = lapply(cover_list_list,function(x)x$cover_0.25)
perc.75_cover = lapply(cover_list_list,function(x)x$cover_0.75)
dist_cover = lapply(cover_list_list,function(x)x$cover_dist)
sigma_delta_sq_mean_list = lapply(cover_list_list,function(x)x$sigma_delta_sq_mean)
sigma_delta_sq_cover = lapply(cover_list_list,function(x)x$cover_sigma_delta_sq)
Sigma_eta_mean_list = lapply(cover_list_list,function(x)x$Sigma_eta_mean)
Sigma_eta_cover= lapply(cover_list_list,function(x)x$cover_Sigma_eta)

length_before = length(GMN_cover)
(time_taken = end_time - start_time)
if(write_dat){
  save(file=dat_name,
     GMN_list,AMN_list,thres_list,AMN_cover,
     GMN_cover,thres_cover, mean_list,median_list,perc.25_list, perc.75_list,dist_list,
     mean_cover,median_cover,perc.25_cover,perc.75_cover,dist_cover,
     sigma_delta_sq_mean_list,sigma_delta_sq_cover,Sigma_eta_mean_list,Sigma_eta_cover,
     check_para,end, K, n, J, sim_num, thin, nIter, burnIn, grid, phi.mat, time_taken,
     Bayesian_Semi_probit)
}

```



# Filter out the null simulations
```{r}
GMN_list = Filter(Negate(is.null), GMN_list)
AMN_list = Filter(Negate(is.null), AMN_list)
thres_list = Filter(Negate(is.null), thres_list)
AMN_cover = Filter(Negate(is.null), AMN_cover)
thres_cover = Filter(Negate(is.null), thres_cover)
GMN_cover = Filter(Negate(is.null), GMN_cover)
mean_list = Filter(Negate(is.null), mean_list)
median_list = Filter(Negate(is.null), median_list)
perc.25_list = Filter(Negate(is.null), perc.25_list)
perc.75_list = Filter(Negate(is.null), perc.75_list)
dist_list = Filter(Negate(is.null), dist_list)
mean_cover = Filter(Negate(is.null), mean_cover)
median_cover = Filter(Negate(is.null), median_cover)
perc.25_cover = Filter(Negate(is.null), perc.25_cover)
perc.75_cover = Filter(Negate(is.null), perc.75_cover)
dist_cover = Filter(Negate(is.null), dist_cover)
sigma_delta_sq_mean_list = Filter(Negate(is.null), sigma_delta_sq_mean_list)
sigma_delta_sq_cover = Filter(Negate(is.null), sigma_delta_sq_cover)
Sigma_eta_mean_list = Filter(Negate(is.null), Sigma_eta_mean_list)
Sigma_eta_cover = Filter(Negate(is.null), Sigma_eta_cover)

length_after =  length(perc.75_cover)
print("# of simulation filter out")
length_before - length_after
```


```{r}
#Cover rate
print("Global mean cover rate")
Reduce("+", mean_cover)/length(mean_cover)
print("Global median cover rate")
Reduce("+", median_cover)/length(median_cover)
print("Global 0.25 perc cover rate")
Reduce("+", perc.25_cover)/length(perc.25_cover)
print("Global 0.75 perc cover rate")
Reduce("+", perc.75_cover)/length(perc.75_cover)
print("Distribution quantity cover rate:  mean   median  perc.25  perc.75 ")
Reduce("+", dist_cover)/length(dist_cover)
print("Alpha cover rate")
Reduce("+", AMN_cover)/length(AMN_cover)
print("Thres cover rate")
Reduce("+", thres_cover)/length(thres_cover)
print("Gamma cover rate")
Reduce("+", GMN_cover)/length(GMN_cover)

#Mean
print("Global mean")
Reduce("+", mean_list)/length(mean_list)
print("Global mean true")
check_para$effect_mean

print("Global median")
Reduce("+", median_list)/length(median_list)
print("Global median true")
check_para$effect_median

print("Global perc 0.25")
Reduce("+", perc.25_list)/length(perc.25_list)
print("Global prec 0.25 true")
check_para$effect_0.25

print("Global perc 0.75")
Reduce("+", perc.75_list)/length(perc.75_list)
print("Global 0.75 true")
check_para$effect_0.75
print("Dist quantity mean")
Reduce("+", dist_list)/length(dist_list)
print("Distribution quantity true")
check_para$effect_dist

print("Alpha mean")
Reduce("+", AMN_list)/length(AMN_list)
print("True Alpha")
check_para$Alpha
print("Thres mean")
Reduce("+", thres_list)/length(thres_list)
print("True thres")
check_para$thres
print("Gamma mean")
Reduce("+", GMN_list)/length(GMN_list)
print("True Gamma")
check_para$Gamma
print("Sigma_delta_sq cover rate")
mean(unlist(sigma_delta_sq_cover))
print("Mean Sigma_delta_sq_mean")
mean(unlist(sigma_delta_sq_mean_list))
print("true Sigma_delta_sq")
check_para$sigma_b_delta^2
print("Simga_eta cover rate")
mean(unlist(Sigma_eta_cover))
print("Mean Simga_eta_mean")
mean(unlist(Sigma_eta_mean_list))
print("true Sigma_eta_square")
check_para$Sigma_b_eta^2
```

# Time consumed
```{r}
end_time - start_time
```

# Supplement material table
# ```{r}
# load("./cover_rate_result_temp_n=40_J=100.R")
# ```

Gamma bias
```{r}
Reduce("+", GMN_list)/length(GMN_list)-check_para$Gamma
```

Gamma sd
```{r}
sqrt(
  Reduce("+", lapply(GMN_list, "^", 2)) / length(GMN_list) - 
       (Reduce("+", GMN_list)/length(GMN_list))^2
  )
```

Gamma cover rate
```{r}
(cover_rate_temp = Reduce("+", GMN_cover)/length(GMN_cover))
```

Gamma cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(GMN_cover))
```

Alpha bias
```{r}
Reduce("+", AMN_list)/length(AMN_list)-check_para$Alpha
```

Alpha sd
```{r}
sqrt(
  Reduce("+", lapply(AMN_list, "^", 2)) / length(AMN_list) - 
       (Reduce("+", AMN_list)/length(AMN_list))^2
  )
```


Alpha cover rate
```{r}
(cover_rate_temp = Reduce("+", AMN_cover)/length(AMN_cover))
```

Alpha cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(AMN_cover))
```

Thres bias
```{r}
Reduce("+", thres_list)/length(thres_list)-check_para$thres
```

Thres sd
```{r}
sqrt(
  Reduce("+", lapply(thres_list, "^", 2)) / length(thres_list) - 
       (Reduce("+", thres_list)/length(thres_list))^2
  )
```

Thres cover rate
```{r}
(cover_rate_temp = Reduce("+", thres_cover)/length(thres_cover))
```

Thres cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(thres_cover))
```

Global random effect variance bias
```{r}
mean(unlist(sigma_delta_sq_mean_list))-check_para$sigma_b_delta^2
```
Global random effect variance sd
```{r}
sqrt(
  Reduce("+", lapply(sigma_delta_sq_mean_list, "^", 2)) / length(sigma_delta_sq_mean_list) - 
       (Reduce("+", sigma_delta_sq_mean_list)/length(sigma_delta_sq_mean_list))^2
  )
```
Global random effect variance coverage rate
```{r}
(cover_rate_temp = mean(unlist(sigma_delta_sq_cover)))
```

Global random effect cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(sigma_delta_sq_cover))
```

Local random effect variance bias
```{r}
mean(unlist(Sigma_eta_mean_list))-check_para$Sigma_b_eta^2
```

Local random effect variance sd
```{r}
sqrt(
  Reduce("+", lapply(Sigma_eta_mean_list, "^", 2)) / length(Sigma_eta_mean_list) - 
       (Reduce("+", Sigma_eta_mean_list)/length(Sigma_eta_mean_list))^2
  )
```

Local random effect variance coverage rate
```{r}
(cover_rate_temp = mean(unlist(Sigma_eta_cover)))
```

Local random effect cover rate MC se
```{r}
sqrt(cover_rate_temp*(1-cover_rate_temp)/length(Sigma_eta_cover))
```

# Result table
True parameters
```{r}
check_para
```

```{r}
# Cover rate
covar_mean_cover = Reduce("+", mean_cover)/length(mean_cover)
covar_median_cover = Reduce("+", median_cover)/length(median_cover)
covar_0.75_cover = Reduce("+", perc.75_cover)/length(perc.75_cover)
dist_name = c("mean", "median",  "perc.25",  "perc.75")
dist_cover1 = Reduce("+", dist_cover)/length(dist_cover)
sigma_b_delta_cover = mean(unlist(sigma_delta_sq_cover))
sigma_b_eta_cover = mean(unlist(Sigma_eta_cover))

# Mean 
covar_mean = Reduce("+", mean_list)/length(mean_list)
covar_median = Reduce("+", median_list)/length(median_list)
covar_0.75 = Reduce("+", perc.75_list)/length(perc.75_list)
dist = Reduce("+", dist_list)/length(dist_list)
sigma_b_delta_mean = mean(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_mean = mean(unlist(Sigma_eta_mean_list))
# Variance 
covar_mean_sd = apply(simplify2array(mean_list), 1:2, sd)
covar_median_sd = apply(simplify2array(median_list), 1:2, sd)
covar_0.75_sd = apply(simplify2array(perc.75_list), 1:2, sd)
dist_sd = apply(simplify2array(dist_list), 1:2, sd)
sigma_b_delta_sd = sd(unlist(sigma_delta_sq_mean_list))
sigma_b_eta_sd = sqrt(
  Reduce("+", lapply(Sigma_eta_mean_list, "^", 2)) / length(Sigma_eta_mean_list) - 
       (Reduce("+", Sigma_eta_mean_list)/length(Sigma_eta_mean_list))^2
  )
  
# True value
covar_mean_true = check_para$effect_mean
covar_median_true = check_para$effect_median
covar_0.75_true = check_para$effect_0.75
dist_true = check_para$effect_dist
sigma_b_delta_true = check_para$sigma_b_delta^2
sigma_b_eta_true = check_para$Sigma_b_eta^2
# Bias
covar_mean_bias = covar_mean-covar_mean_true
covar_median_bias =covar_median - covar_median_true
covar_0.75_bias = covar_0.75 - covar_0.75_true
dist_bias = dist - dist_true
sigma_b_delta_bias = sigma_b_delta_mean-sigma_b_delta_true
sigma_b_eta_bias = sigma_b_eta_mean-sigma_b_eta_true
# Building the table
d = data.frame(names = c(paste(rep("mean",3), c("intercept", "X1", "X2")),
                     paste(rep("median",3), c("intercept", "X1", "X2")),
                     paste(rep("0.75",3), c("intercept", "X1", "X2")),
                     paste(rep("distribution", 4), dist_name)
                     ),
           bias = c(covar_mean_bias, covar_median_bias, 
                    covar_0.75_bias,dist_bias
                    ),
           sd = c(covar_mean_sd, covar_median_sd,
                  covar_0.75_sd, dist_sd
                  ),
           coverage_probability = c(
             covar_mean_cover, covar_median_cover, 
             covar_0.75_cover,dist_cover1
           ),
           True_value = c(
             covar_mean_true,covar_median_true,
             covar_0.75_true,dist_true
           ),
           mean = c(
             covar_mean,covar_median,
             covar_0.75, dist
           )) %>% 
  mutate(MC_se = sqrt(coverage_probability * (1-coverage_probability)/length_after))
knitr::kable(d)
if(write_dat){
  write.csv(d, file = table_name)
}
```

```{r}
print(Bayesian_Semi_probit)
```

